Effects of Reynolds Number on the Performance and Near-Wake Dynamics of a Vertical-Axis Cross-Flow Turbine

### 2015-09-03 paper.tex
Scale down figure
changeto secind sentence of Introduction (test edit & commit)

Scaled physical models are often used in science and engineering to approximate
real-world systems. However, the principle of dynamic similarity allows for
geometrically scaled systems to be dynamically identical in scale if certain
nondimensional physical parameters are matched. In the case of fluid systems,
the most important parameter is often the Reynolds number, which quantifies the
importance of viscosity on the flow physics. As such, hereafter we will use the
word ``scale'' to refer to this dynamical scale rather than the geometric scale.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.95\textwidth]{figures/perf_re_dep}
\caption{Mean power (left) and drag (right) coefficients at $\lambda=1.9$
plotted versus Reynolds number.} 
\label{fig:perf-Re-dep}
\end{figure}

>>>>

Scaled physical models are often used in science and engineering to approximate
real-world systems. The principle of dynamic similarity allows for geometrically
scaled systems to be dynamically similar in scale if certain nondimensional
physical parameters are matched. In the case of fluid systems, the most
important parameter is often the Reynolds number, which quantifies the
importance of viscosity on the flow physics. As such, hereafter we will use the
word ``scale'' to refer to this dynamical scale rather than the geometric scale.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.9\textwidth]{figures/perf_re_dep}
\caption{Mean power (left) and drag (right) coefficients at $\lambda=1.9$
plotted versus Reynolds number.} 
\label{fig:perf-Re-dep}
\end{figure}
